### 2020-07-17 article.tex
Some more typo
Some more remarks

\pk{KSPHPDDM}, the interface between HPDDM Krylov methods and PETSc, is automatically
registered since PETSc version 3.12 when configuring PETSc with the extra
flag \pk{-{}-download-hpddm}. HPDDM linear solvers can be selected using the command
line option \pk{-ksp\_type hpddm}, or the routine \pk{KSPSetType}(ksp,
\pk{KSPHPDDM}), and the following Krylov methods can be accessed:
\begin{itemize}
    \item pseudo-block GMRES or flexible GMRES~\cite{saad1993flexible};
    \item pseudo-block CG or flexible CG~\cite{notay2000flexible};
    \item pseudo-block GCRODR or flexible GCRODR~\cite{carvalho2011flexible};
    \item block GMRES or flexible GMRES~\cite{calandra2012flexible};
    \item block CG~\cite{o1980block};
    \item breakdown-free block CG~\cite{ji2017breakdown};
    \item block GCRODR or flexible GCRODR.
\end{itemize}
While being mathematically equivalent to
their ``standard'' counterparts, the pseudo-block variants try to fuse together multiple similar
operations like matrix--vector
products to achieve higher arithmetic intensity, or to decrease the
number of global synchronizations needed for scalar products.
HPDDM Krylov methods may be selected {\color{red} TODO API FOR KSPHPDDMSetVariant?} using the
options \pk{-ksp\_hpddm\_type}
\pk{(gmres$|$cg$|$gcrodr$|$bgmres$|$bcg$|$bfbcg$|$bgcrodr$|$preonly)}, or the
routine \pk{KSPHPDDMSetType}(ksp, \pk{KSPHPDDMType}).
Preconditioning variants can be specified via
\pk{-ksp\_hpddm\_variant} \pk{(left$|$right$|$flexible)} to select whether the
preconditioner is applied on the left, on the right, or if it cannot be
represented as a linear operator. In this latter case, the preconditioner is
always applied on the right, except for FCG. HPDDM CG
and its variants BCG and BFBCG only handle left-preconditioning.  It is also
possible to set the preconditioning side through the more common PETSc option
\pk{-ksp\_pc\_side (left$|$right)}.  Finally, convergence monitoring with the
\pk{KSPMonitor} interface is fully supported, as well as the specification of
customized convergence testing via the \pk{KSPSetConvergenceTest} callback.

According to the standard PETSc notation, ksp($A$, $P_{A'}$)
defines a \pk{KSP} used to solve a system $Ax=b$ using a preconditioner $P_{A'}$ built
using an operator $A'$ which is usually, but not necessarily, equal to $A$. While solving
the linear system via \pk{KSPSolve}(ksp, $b$, $x$) or \pk{KSPMatSolve}(ksp, $B$, $X$),
HPDDM will repeatedly call the following PETSc routines:
\begin{itemize}
    \item \pk{MatMult}($A$, $x$, $y$) for $y = Ax$;
    \item \pk{MatMatMult}($A$, $X$, {\small \pk{MAT\_REUSE\_MATRIX}}, {\small
        \pk{PETSC\_DEFAULT}}, $Y$)\footnote{or \pk{MatProductNumeric}($Y$) with PETSc 3.14.0 and above} for $Y =
        AX$;
    \item \pk{PCApply}($P_{A'}$, $x$, $y$) for $y = P_{A'}x$;
    \item \pk{PCMatApply}($P_{A'}$, $X$, $Y$) for $Y = P_{A'}X$;
\end{itemize}
As of version 3.14.0, PETSc provides unified routines for applying $A$ or $P_{A'}$
to a tall-and-skinny dense matrix $X$. However, when no specialized implementation
is available, PETSc will loop over the columns of $X$ and successively apply $A$
or $P_{A'}$ to get all columns of $Y$. For matrix--matrix products, there are
currently specialized implementations for the following \pk{MatType}:
\begin{itemize}
    \item \pk{MatSeqAIJ}, standard sequential sparse matrix, based on compressed sparse row format;
    \item \pk{MatSeqBAIJ}, block sparse matrix, based on block compressed sparse row format;
    \item \pk{MatSeqSBAIJ}, symmetric block sparse matrix stored in upper triangular form.
    \item \pk{MatMPIAIJ}, standard parallel sparse matrix;
    \item \pk{MatShell}, user-defined matrix;
    \item \pk{MatNest}, block-defined matrix with nested submatrices;
    \item \pk{MatSeqAIJCUSPARSE}, standard sequential sparse matrix, offloaded to a GPU using cuSPARSE~\cite{cusparse-web-page}.
\end{itemize}
The following preconditioners have specialized implementations for dealing
efficiently with multiple vectors:
\begin{enumerate}
    \item \pk{PCNONE}: $P_{A'} = I$, identity matrix;
    \item \pk{PCKSP}: embedded Krylov method inside $P_{A'}$;
    \item \pk{PCMAT}: multiplication by $A'$, i.e., $P_{A'} = {A'}$;
    \item \pk{PCSHELL}: user-defined preconditioner, e.g., matrix-free;
    % \item \pk{PCSPAI}: sparse approximate inverse~\cite{grote1997parallel};
    \item \pk{PCHARA}~\cite{10.1145/3232850};
    \item \pk{PCHPDDM}: see~\cref{sec:PCHPDDM};\label{it:hpddm}
    \item \pk{PCASM} and \pk{PCGASM}: overlapping Schwarz methods;\label{it:asm}
    \item \pk{PCBJACOBI}: block Jacobi;\label{it:bjacobi}
    \item \pk{PCLU} or \pk{PCCHOLESKY}: exact $LU$ or Cholesky factorization,
        e.g., $P_{A'} = {L}^{-1}{U}^{-1}$;\label{it:lu}
    \item \pk{PCILU} or \pk{PCICC}: incomplete $LU$ or Cholesky
        factorization.\label{it:ilu}
\end{enumerate}
One appealing feature of domain decomposition-like preconditioners 
\cref{it:hpddm,it:asm,it:bjacobi} is that they most often rely on exact or inexact
factorizations~\cref{it:lu,it:ilu} as subdomain solvers.
In these cases, it is possible to access the so-called local or distributed factored matrix $F$
%via \pk{PCFactorGetMatrix} and then call \pk{MatMatSolve}($F$, $\tilde{Y}$, $\tilde{X}$).
via \pk{PCFactorGetMatrix}, and then call \pk{MatMatSolve}($F$, $X$, $Y$) to take advantage
of blocked forward eliminations and backward substitutions from the various factorization packages
interfaced with PETSc. In the case of a sparse coefficient matrix $A'$,
this strategy is possible with: MUMPS~\cite{amestoy2001fully},
SuiteSparse~\cite{davis2004algorithm}, MKL
PARDISO or CPARDISO~\cite{mkl-web-page}, and SuperLU~\cite{li2005overview} or
SuperLU\_DIST~\cite{li2003superlu_dist}. For the case of a dense coefficient
matrix $A'$: ScaLAPACK and Elemental~\cite{poulson2013elemental}. 
Future work will consider extending the various implementations of PETSc
preconditioning infrastructure to increase the arithmetic intensity of the
block preconditioner application phase.

@@

For performance reasons, it is better to compute the same number of
eigenvectors on each process, since in this case the coarse operator will be
assembled using the \pk{MatMPISBAIJ} or \pk{MatMPIBAIJ} matrix type, with
usually large block sizes. This can have serious memory and performance
implications, see~\cref{fig:perfAX}. When applying the preconditioner,
\texttt{MPI\_Gather} and \texttt{MPI\_Scatter} operations are used to move
between levels, instead of the variable-size alternatives \texttt{MPI\_Gatherv}
and \texttt{MPI\_Scatterv}, that could exhibit worse performance. In addition,
standard eigensolvers such as ARPACK~\cite{lehoucq1998arpack} or
\pk{EPSKRYLOVSCHUR} from SLEPc, cannot cheaply evaluate the exact number of eigenpairs in a given
interval of $\mathbb{R}^+$. Instead, it is often more efficient to provide an upper bound of the number of eigenpairs.

@@

explained \pk{PCHPDDMSetAuxiliaryMat} function, this is done automatically if the nonliear solver is attached to a

@@

\bibitem{lehoucq1998arpack}
{\sc R.~Lehoucq, D.~Sorensen, and C.~Yang}, {\em {ARPACK} users’ guide\col\
  solution of large-scale eigenvalue problems with implicitly restarted Arnoldi
  methods}, vol.~6, Society for Industrial and Applied Mathematics, 1998,
  \url{http://www.caam.rice.edu/software/ARPACK}.

>>>>

\pk{KSPHPDDM}, the interface between HPDDM Krylov methods and PETSc, is automatically
registered since PETSc version 3.12 when configuring PETSc with the extra
flag \pk{-{}-download-hpddm}. HPDDM linear solvers can be selected using the command
line option \pk{-ksp\_type hpddm}, or the routine \pk{KSPSetType}(ksp,
\pk{KSPHPDDM}), and the following Krylov methods can be accessed:
\begin{itemize}
    \item pseudo-block GMRES or flexible GMRES~\cite{saad1993flexible};
    \item pseudo-block CG or flexible CG~\cite{notay2000flexible};
    \item pseudo-block GCRODR or flexible GCRODR~\cite{carvalho2011flexible};
    \item block GMRES or flexible GMRES~\cite{calandra2012flexible}, with deflation at each restart;
    \item block CG~\cite{o1980block};
    \item breakdown-free block CG~\cite{ji2017breakdown}, with deflation at each iteration;
    \item block GCRODR or flexible GCRODR, with deflation at each restart.
\end{itemize}
While being mathematically equivalent to
their ``standard'' counterparts, the pseudo-block variants try to fuse together multiple similar
operations like matrix--vector
products to achieve higher arithmetic intensity, or to decrease the
number of global synchronizations needed for scalar products.
HPDDM Krylov methods may be selected {\color{red} TODO API FOR KSPHPDDMSetVariant?} using the
options \pk{-ksp\_hpddm\_type}
\pk{(gmres$|$cg$|$gcrodr$|$bgmres$|$bcg$|$bfbcg$|$bgcrodr$|$preonly)}, or the
routine \pk{KSPHPDDMSetType}(ksp, \pk{KSPHPDDMType}).
Preconditioning variants can be specified via
\pk{-ksp\_hpddm\_variant} \pk{(left$|$right$|$flexible)} to select whether the
preconditioner is applied on the left, on the right, or if it cannot be
represented as a linear operator. In this latter case, the preconditioner is
always applied on the right, except for FCG. HPDDM CG
and its variants BCG and BFBCG only handle left-preconditioning.  It is also
possible to set the preconditioning side through the more common PETSc option
\pk{-ksp\_pc\_side (left$|$right)}.  Finally, convergence monitoring with the
\pk{KSPMonitor} interface is fully supported, as well as the specification of
customized convergence testing via the \pk{KSPSetConvergenceTest} callback.

According to the standard PETSc notation, ksp($A$, $P_{A'}$)
defines a \pk{KSP} used to solve a system $Ax=b$ using a preconditioner $P_{A'}$ built
using an operator $A'$ which is usually, but not necessarily, equal to $A$. While solving
the linear system via \pk{KSPSolve}(ksp, $b$, $x$) or \pk{KSPMatSolve}(ksp, $B$, $X$),
HPDDM will repeatedly call the following PETSc routines:
\begin{itemize}
    \item \pk{MatMult}($A$, $x$, $y$) for $y = Ax$;
    \item \pk{MatMatMult}($A$, $X$, {\small \pk{MAT\_REUSE\_MATRIX}}, {\small
        \pk{PETSC\_DEFAULT}}, $Y$)\footnote{or \pk{MatProductNumeric}($Y$) with PETSc 3.14.0 and above} for $Y =
        AX$;
    \item \pk{PCApply}($P_{A'}$, $x$, $y$) for $y = P_{A'}x$;
    \item \pk{PCMatApply}($P_{A'}$, $X$, $Y$) for $Y = P_{A'}X$;
\end{itemize}
As of version 3.14.0, PETSc provides unified routines for applying $A$ or $P_{A'}$
to a tall-and-skinny dense matrix $X$. However, when no specialized implementation
is available, PETSc will loop over the columns of $X$ and successively apply $A$
or $P_{A'}$ to get all columns of $Y$. For matrix--matrix products, there are
currently specialized implementations for the following \pk{MatType}:
\begin{itemize}
    \item \pk{MatSeqAIJ}, standard sequential sparse matrix, based on compressed sparse row format;
    \item \pk{MatSeqBAIJ}, block sparse matrix, based on block compressed sparse row format;
    \item \pk{MatSeqSBAIJ}, symmetric block sparse matrix stored in upper triangular form.
    \item \pk{MatMPIAIJ}, standard parallel sparse matrix;
    \item \pk{MatShell}, user-defined matrix;
    \item \pk{MatNest}, block-defined matrix with nested submatrices;
    \item \pk{MatSeqAIJCUSPARSE}, standard sequential sparse matrix, offloaded to a GPU using cuSPARSE~\cite{cusparse-web-page}.
\end{itemize}
The following preconditioners have specialized implementations for dealing
efficiently with multiple vectors:
\begin{enumerate}
    \item \pk{PCNONE}: $P_{A'} = I$, identity matrix;
    \item \pk{PCKSP}: embedded Krylov method inside $P_{A'}$;
    \item \pk{PCMAT}: multiplication by $A'$, i.e., $P_{A'} = {A'}$;
    \item \pk{PCSHELL}: user-defined preconditioner, e.g., matrix-free;
    % \item \pk{PCSPAI}: sparse approximate inverse~\cite{grote1997parallel};
    \item \pk{PCHARA}~\cite{10.1145/3232850};
    \item \pk{PCHPDDM}: see~\cref{sec:PCHPDDM};\label{it:hpddm}
    \item \pk{PCASM} and \pk{PCGASM}: overlapping Schwarz methods;\label{it:asm}
    \item \pk{PCBJACOBI}: block Jacobi;\label{it:bjacobi}
    \item \pk{PCLU} or \pk{PCCHOLESKY}: exact $LU$ or Cholesky factorization,
        e.g., $P_{A'} = {U}^{-1}{L}^{-1}$;\label{it:lu}
    \item \pk{PCILU} or \pk{PCICC}: incomplete $LU$ or Cholesky
        factorization.\label{it:ilu}
\end{enumerate}
One appealing feature of domain decomposition-like preconditioners 
\cref{it:hpddm,it:asm,it:bjacobi} is that they most often rely on exact or inexact
factorizations~\cref{it:lu,it:ilu} as subdomain solvers.
In these cases, it is possible to access the so-called local or distributed factored matrix $F$
%via \pk{PCFactorGetMatrix} and then call \pk{MatMatSolve}($F$, $\tilde{Y}$, $\tilde{X}$).
via \pk{PCFactorGetMatrix}, and then call \pk{MatMatSolve}($F$, $X$, $Y$) to take advantage
of blocked forward eliminations and backward substitutions from the various factorization packages
interfaced with PETSc. In the case of a sparse coefficient matrix $A'$,
this strategy is possible with: MUMPS~\cite{amestoy2001fully},
SuiteSparse~\cite{davis2004algorithm}, MKL
PARDISO or CPARDISO~\cite{mkl-web-page}, and SuperLU~\cite{li2005overview} or
SuperLU\_DIST~\cite{li2003superlu_dist}. For the case of a dense coefficient
matrix $A'$: ScaLAPACK and Elemental~\cite{poulson2013elemental}. 
Future work will consider extending the various implementations of PETSc
preconditioning infrastructure to increase the arithmetic intensity of the
block preconditioner application phase.

@@

For performance reasons, it is better to compute the same number of
eigenvectors on each process, since in this case the coarse operator will be
assembled using the \pk{MatMPISBAIJ} or \pk{MatMPIBAIJ} matrix type, with
usually large block sizes. This can have serious memory and performance
implications, see~\cref{fig:perfAX}. When applying the preconditioner,
\texttt{MPI\_Gather} and \texttt{MPI\_Scatter} operations are used to move
between levels, instead of the variable-size alternatives \texttt{MPI\_Gatherv}
and \texttt{MPI\_Scatterv}, that could exhibit worse performance. In addition,
standard eigensolvers such as \pk{EPSKRYLOVSCHUR} from SLEPc, cannot cheaply
evaluate the exact number of eigenpairs in a given interval of $\mathbb{R}^+$.
Instead, it is often more efficient to provide an upper bound of the number of
eigenpairs.

@@

explained \pk{PCHPDDMSetAuxiliaryMat} function, this is done automatically if the nonlinear solver is attached to a

@@
